The Unified Nature of the Dielectric Properties of Two-Dimensional Materials

### 2018-11-15 paper.tex
Add optical bandgap in SI

@@

Here we show that instead of the dielectric constant $\varepsilon$,
the 2D polarizabilty $\alpha$ correctly captures the dielectric nature

@@

$\alpha^{\parallel}$ is inversely proportional to the minimal bandgap

@@

$\alpha^{\perp}$ is directly related with the thickness

@@

$\boldsymbol{u} = {\displaystyle \int_{\mathrm{SL}}
  \rho(\boldsymbol{r}) \boldsymbol{r}^{p} d^{3}\boldsymbol{r}}$ is the
total dipole moments of the SL, $\rho$ is the spatial charge density,
$\Omega=AL$ is the volume, $A$ is the xy-plane area of the SL and
$\varepsilon_{0}$ is vacuum permittivity. For the majority of 2D
semiconductors, the off-diagonal elements of the dielectric tensor
($p \neq q$) tend to be negligible.  Considering that the 2D material
is placed in vacuum ($\kappa^{pp} = 1$ and $\kappa^{pq} = 0$), we can
distinguish two components, namely the in-plane
($\varepsilon_{\mathrm{SL}}^{\parallel}$) and out-of-plane

@@

Supplementary Figure SXX \todo{check}, the charge density difference

@@

SXX \todo{xxx}.

% It is also worth mentioning that the dielectric properties of 2D
% materials are also often modeled using an effective medium approach,
% which treats the 2D material as a slab with effective permittivity
% $\varepsilon_{\mathrm{2D}}$ and thickness $\delta$
% \cite{Sharma_1985,Cudazzo_2011_screening_2D,Matthes_2016,Trolle_2017_eps_subst,Laturia_2018}. Such
% methods require \textit{a priori} determination of $\delta$, a
% quantity with controversial definitions \cite{Mas_Ballest__2011}. In
% such approaches, $\varepsilon_{\mathrm{2D}}$ and $\delta$ have to be
% determined by fitting the $L$-dependent data of
% $\varepsilon_{\mathrm{SL}}$, which is not only computational
% expensive, but also fails to capture the anisotropy of the 2D
% dielectric properties (see Supplementary Section S1). On the other
% hand, calculating 2D polarizabilities requires no knowledge of
% $\delta$ (see Eqs. \ref{eq:alpha-para-def} and
% \ref{eq:alpha-perp-def}), and correctly presents the anisotropy of 2D
% dielectric nature that $\alpha^{\parallel} > \alpha^{\perp}$.  With
% the polarizability as the true descriptor of 2D dielectric properties,
% we will reveal the universal Moss-like relation of 2D materials from
% both theoretical and first principles studies.

@@

$E_{\mathrm{g}}$ is observed (see Supplementary Section S2.2), which
appears to be in good agreement with our polarizability-based
theoretical model (Supplementary Section SXX \todo{note}). We then
examine Eqs. \ref{eq:2D-Moss-para} and \ref{eq:2D-Moss-perp} using the
polarizabilities calculated by first principle calculations. Figure
\ref{fig-3}b shows

@@

$(4 \pi \varepsilon_{0})/\alpha_{\mathrm{2D}}^{\parallel}$ and $E_{\mathrm{g}}$
(measured by the $R^{2}$ value) is higher when the bandgap is
calculated using the HSE06 hybrid functionals, compared with that from
the Perdew--Burk--Ernzerhof (PBE) exchange correlations (details see
Supplementary Section S2 and Supplementary Figure S5), which can be

@@

$\alpha_{\mathrm{2D}}^{\parallel}$ and $E_{\mathrm{g}}$.
\todo[inline]{check the values for optical bandgap}

>>>>

\usepackage{xr}
\externaldocument[SI-]{SI}

@@

Here we show that instead of the dielectric constant,
the 2D polarizabilty correctly captures the dielectric nature

@@

$\alpha^{\parallel}_{\mathrm{2D}}$ is inversely proportional to the minimal bandgap

@@

$\alpha^{\perp}_{\mathrm{2D}}$ is directly related with the thickness

@@

$\boldsymbol{u}$ is the total dipole moments within the SL, $\rho$ is the
spatial charge density, $\Omega=AL$ is the volume, $A$ is the xy-plane
area of the SL and $\varepsilon_{0}$ is vacuum permittivity. For the
majority of 2D semiconductors, the off-diagonal elements of the
dielectric tensor ($p \neq q$) tend to be negligible.  Considering
that the 2D material is placed in vacuum ($\kappa^{pp} = 1$ and
$\kappa^{pq} = 0$), we can distinguish two components, namely the
in-plane ($\varepsilon_{\mathrm{SL}}^{\parallel}$) and out-of-plane

@@

Supplementary Figure \ref{SI-fig:rho-profile}, the charge density difference

@@

\ref{SI-sec:2D-3D-rescale}.

@@

$E_{\mathrm{g}}$ is observed (see Supplementary Section
\ref{SI-sec:pol-2D-Eg}), which appears to be in good agreement with
our polarizability-based theoretical model (Supplementary Section SXX
\todo{note}). We then examine Eqs. \ref{eq:2D-Moss-para} and
\ref{eq:2D-Moss-perp} using the polarizabilities calculated by first
principle calculations. Figure \ref{fig-3}b shows

@@

$(4 \pi \varepsilon_{0})/\alpha_{\mathrm{2D}}^{\parallel}$ and
$E_{\mathrm{g}}$ (measured by the $R^{2}$ value) is higher when the
bandgap is calculated using the HSE06 hybrid functionals, compared
with that from the Perdew--Burk--Ernzerhof (PBE) exchange correlations
(details see Supplementary Section \ref{SI-sec:pol-2D-Eg} and
Supplementary Figure \ref{SI-fig:alpha-Eg-diff}), which can be

@@

$\alpha_{\mathrm{2D}}^{\parallel}$ and $E_{\mathrm{g}}$. We also show
that the proposed relation behaves equivalently well when using the
experimentally accessible optical bandgap of 2D materials (details see
Supplementary Section \ref{SI-sec:gpaw-2} and Supplementary Figure
\ref{SI-fig:opt}).
